Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions

### 2019-08-13 Manuscript/Manuscript.Rmd
updating w MAD analyses
many changes

### make long ###
data.long <- gather(data, key = "Condition", value = "ReactionTime",
                    lo.neu.sur_n_RT, hi.neu.sur_n_RT,
                    lo.emo.sur_n_RT, hi.emo.sur_n_RT,
                    lo.neu.sur_p_RT, hi.neu.sur_p_RT,
                    lo.emo.sur_p_RT, hi.emo.sur_p_RT)
data.long$Condition <- as.factor(data.long$Condition)

data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars="Condition", na.rm = TRUE)

ggplot(data.long.summary, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
  geom_errorbar(aes(ymin=ReactionTime-se, ymax=ReactionTime+se), width=.1)

@@

``` {r MAD, include = FALSE}
###  MAD analyses ###
results.long <- gather(data, key = "Condition", value = "MAD",
                       lo.emo.sur_MAD, hi.emo.sur_MAD, lo.neu.sur_MAD, hi.neu.sur_MAD)
results.long$load <- ifelse(results.long$Condition == "lo.emo.sur_MAD", "Low",
                            ifelse(results.long$Condition == "lo.neu.sur_MAD", "Low", "High"))
results.long$type <- ifelse(results.long$Condition == "lo.emo.sur_MAD", "Emo",
                            ifelse(results.long$Condition == "hi.emo.sur_MAD", "Emo", "Neu"))

@@

``` {r MAD plot, include = TRUE}
ggplot(res.long.sum, aes(Condition, MAD, fill = as.factor(Condition))) +
  geom_bar(stat = "summary", fun.y = "mean") +
  geom_errorbar(aes(ymin=`MAD`-se, ymax=`MAD`+se), width=.1)
```
Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.

>>>>

### make long ###
data.long <- gather(data, key = "Condition", value = "ReactionTimeZ",
                    lo.neu.sur_n_RTz, hi.neu.sur_n_RTz,
                    lo.emo.sur_n_RTz, hi.emo.sur_n_RTz,
                    lo.neu.sur_p_RTz, hi.neu.sur_p_RTz,
                    lo.emo.sur_p_RTz, hi.emo.sur_p_RTz)
data.long$Condition <- as.factor(data.long$Condition)

data.long.summary <- summarySE(data.long, measurevar="ReactionTimeZ", groupvars="Condition", na.rm = TRUE)

ggplot(data.long.summary, aes(Condition, ReactionTimeZ, fill = as.factor(Condition))) +
  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
  geom_errorbar(aes(ymin=ReactionTimeZ-se, ymax=ReactionTimeZ+se), width=.1)

@@

``` {r MAD, include = FALSE}
###  MAD analyses ###
### check for normality ###
shapiro.test(data$lo.emo.sur_MAD) # barely normal (p = .054)
shapiro.test(data$hi.emo.sur_MAD) # barely normal (p = .08)
shapiro.test(data$lo.neu.sur_MAD) # normal
shapiro.test(data$hi.neu.sur_MAD) # normal

results.long <- gather(data, key = "Condition", value = "MAD",
                       lo.emo.sur_MAD, hi.emo.sur_MAD, lo.neu.sur_MAD, hi.neu.sur_MAD)
results.long$load <- ifelse(results.long$Condition == "lo.emo.sur_MAD", "Low",
                            ifelse(results.long$Condition == "lo.neu.sur_MAD", "Low", "High"))
results.long$type <- ifelse(results.long$Condition == "lo.emo.sur_MAD", "Emo",
                            ifelse(results.long$Condition == "hi.emo.sur_MAD", "Emo", "Neu"))

@@

``` {r MAD plot, include = TRUE}
ggplot(res.long.sum, aes(Condition, MAD, fill = as.factor(Condition))) +
  geom_bar(stat = "summary", fun.y = "mean") +
  geom_errorbar(aes(ymin=`MAD`-se, ymax=`MAD`+se), width=.1)
```
``` {r MAD map}
suppressPackageStartupMessages(library(mousetrap)) 
# source MADFigure.R ???

```
Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.
